Data Analysis Extensions

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view1.tex
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

\tikzstyle{groupBox} = [draw, ellipse, fill=white, minimum size=20pt,
  text centered, font=\footnotesize\sffamily, text width=20pt, inner sep=0]

\tikzstyle{textBox} = [fill=white, inner sep=2pt, text centered, font=\footnotesize\sffamily]

@@

% Root
\node[groupBox] (root) {root};

@@

% Datasets
% G0
\node[below=30pt of group0, inner sep=0] (datasetg0) {};
\node[rectangle, text height=25pt, left=40pt of datasetg0, inner sep=0] (tempg0) {};
\drawdataset{shift=(tempg0.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg0, inner sep=0] (presg0) {};
\drawdataset{shift=(presg0.south), scale=0.3}

% G1
\node[below=30pt of group1, inner sep=0] (datasetg1) {};
\node[rectangle, text height=25pt, left=40pt of datasetg1, inner sep=0] (tempg1) {};
\drawdataset{shift=(tempg1.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg1, inner sep=0] (presg1) {};
\drawdataset{shift=(presg1.south), scale=0.3}

% G2
\node[below=30pt of group2, inner sep=0] (datasetg2) {};
\node[rectangle, text height=25pt, left=40pt of datasetg2, inner sep=0] (tempg2) {};
\drawdataset{shift=(tempg2.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg2, inner sep=0] (presg2) {};
\drawdataset{shift=(presg2.south), scale=0.3}

>>>>

\tikzstyle{groupBox} = [draw, ellipse, fill=white, minimum size=20pt,
  text centered, font=\sffamily, text width=20pt, inner sep=0]

\tikzstyle{textBox} = [fill=white, inner sep=2pt, text centered, font=\sffamily]

@@

% Root
\node[groupBox] (root) {/};

@@

% Datasets
% G0
\node[below=30pt of group0, inner sep=0] (datasetg0) {};
\node[rectangle, text height=25pt, left=45pt of datasetg0, inner sep=0] (tempg0) {};
\drawdataset{shift=(tempg0.south), scale=0.3}
\node[rectangle, text height=25pt, right=45pt of datasetg0, inner sep=0] (presg0) {};
\drawdataset{shift=(presg0.south), scale=0.3}

% G1
\node[below=30pt of group1, inner sep=0] (datasetg1) {};
\node[rectangle, text height=25pt, left=45pt of datasetg1, inner sep=0] (tempg1) {};
\drawdataset{shift=(tempg1.south), scale=0.3}
\node[rectangle, text height=25pt, right=45pt of datasetg1, inner sep=0] (presg1) {};
\drawdataset{shift=(presg1.south), scale=0.3}

% G2
\node[below=30pt of group2, inner sep=0] (datasetg2) {};
\node[rectangle, text height=25pt, left=45pt of datasetg2, inner sep=0] (tempg2) {};
\drawdataset{shift=(tempg2.south), scale=0.3}
\node[rectangle, text height=25pt, right=45pt of datasetg2, inner sep=0] (presg2) {};
\drawdataset{shift=(presg2.south), scale=0.3}

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view4.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

\def\drawdataset#1{%
\begin{scope}[#1]
  \foreach \y in {-1.5,-0.5,0.5} {
      \foreach \x in {-2.5,-1.5,-0.5,0.5,1.5} {
          \pgfmathparse{less(50,rnd*70)*100}
          \pgfmathtruncatemacro{\fillcolor}{\pgfmathresult}
          \colorlet{selectcolor}{rulecolor!\fillcolor!white}
          \path[fill=selectcolor, draw] (\x,\y) rectangle ++(1,1);
      }
  }
\end{scope}
}

@@

% Datasets
% G0
\node[below=30pt of group0, inner sep=0] (datasetg0) {};
\node[rectangle, text height=25pt, left=40pt of datasetg0, inner sep=0] (tempg0) {};
\drawdataset{shift=(tempg0.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg0, inner sep=0] (presg0) {};
\drawdataset{shift=(presg0.south), scale=0.3}

% G1
\node[below=30pt of group1, inner sep=0] (datasetg1) {};
\node[rectangle, text height=25pt, left=40pt of datasetg1, inner sep=0] (tempg1) {};
\drawdataset{shift=(tempg1.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg1, inner sep=0] (presg1) {};
\drawdataset{shift=(presg1.south), scale=0.3}

% G2
\node[below=30pt of group2, inner sep=0] (datasetg2) {};
\node[rectangle, text height=25pt, left=40pt of datasetg2, inner sep=0] (tempg2) {};
\drawdataset{shift=(tempg2.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg2, inner sep=0] (presg2) {};
\drawdataset{shift=(presg2.south), scale=0.3}

>>>>

\def\drawdataset#1#2{%
\begin{scope}[#1]
  \foreach \y in {-1.5,-0.5,0.5} {
      \foreach \x in {-2.5,-1.5,-0.5,0.5,1.5} {
          \pgfmathparse{less(50,rnd*70)*100}
          \pgfmathtruncatemacro{\fillcolor}{\pgfmathresult}
          \colorlet{selectcolor}{#2!\fillcolor!white}
          \path[fill=selectcolor, draw] (\x,\y) rectangle ++(1,1);
      }
  }
\end{scope}
}

@@

% Datasets
% G0
\node[below=30pt of group0, inner sep=0] (datasetg0) {};
\node[rectangle, text height=25pt, left=45pt of datasetg0, inner sep=0] (tempg0) {};
\drawdataset{shift=(tempg0.south), scale=0.3}{white}
\node[rectangle, text height=25pt, right=45pt of datasetg0, inner sep=0] (presg0) {};
\drawdataset{shift=(presg0.south), scale=0.3}{rulecolor}

% G1
\node[below=30pt of group1, inner sep=0] (datasetg1) {};
\node[rectangle, text height=25pt, left=45pt of datasetg1, inner sep=0] (tempg1) {};
\drawdataset{shift=(tempg1.south), scale=0.3}{white}
\node[rectangle, text height=25pt, right=45pt of datasetg1, inner sep=0] (presg1) {};
\drawdataset{shift=(presg1.south), scale=0.3}{rulecolor}

% G2
\node[below=30pt of group2, inner sep=0] (datasetg2) {};
\node[rectangle, text height=25pt, left=45pt of datasetg2, inner sep=0] (tempg2) {};
\drawdataset{shift=(tempg2.south), scale=0.3}{white}
\node[rectangle, text height=25pt, right=45pt of datasetg2, inner sep=0] (presg2) {};
\drawdataset{shift=(presg2.south), scale=0.3}{rulecolor}
